[DRAFT] Tipologi Kerentanan Iklim pada Penghidupan Berbasis Pertanian: Sulawesi Selatan

### 2023-11-06 draft_fgd_tipologi_kerentanan_sulsel.qmd
fix missing images

---
title: "[DRAFT] Tipologi Kerentanan Iklim pada Penghidupan Berbasis Pertanian: Sulawesi Selatan"
format: 
  html:
    toc: true
    number-sections: true
editor: visual
execute:
  echo: false
project:
  type: website
  output-dir: docs
editor_options: 
  chunk_output_type: inline
comments:
  utterances:
    repo: icraf-indonesia/vulnerability-typology-map
---

>>>>

---
title: "[DRAFT] Tipologi Kerentanan Iklim pada Penghidupan Berbasis Pertanian: Sulawesi Selatan"
format: 
  html:
    toc: true
    number-sections: true
    self-contained: true
editor: visual
execute:
  echo: false
project:
  type: website
  output-dir: docs
editor_options: 
  chunk_output_type: inline
comments:
  utterances:
    repo: icraf-indonesia/vulnerability-typology-map
---
